\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{OM SONAWANE} % Your name
\address{Front-End Developer \\ UI/UX Designer} 
\address{\href{mailto:omsonawane03@gmail.com}{omsonawane03@gmail.com} \\ \href{https://www.linkedin.com/in/om-sonawane-23bab11b8/}{linkedin} \\ \href{https://github.com/om-sonawane}{github}}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFILE
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFILE}

Final year B. Tech in Computer Science and Engineering student with multiple web development projects demonstrating my ability to design and implement responsive, user-friendly websites and applications using modern web technologies. Proficient in HTML, CSS, C, and C++, tackling diverse software development challenges.

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills: & C, C++, HTML, CSS, JavaScript, Python, Java, SQL, PHP. \\
Tools: & Figma, Canva, WordPress, Photoshop \\
Industry Skills: & Web Development, Database Management, User Interface Design, Software Development \\
\end{tabular}

\end{rSection}

%---------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Intern} \hfill Dec 2022 - Jan 2023 \\
IT-DIGI SOLUTION, Jalgaon
\begin{itemize}
    \item Developed and customized WordPress websites, resulting in a 30\% increase in user engagement.
    \item Implemented various web development tasks, including theme and plugin customization, which improved website loading speed by 25\%. 
\end{itemize}

\textbf{Intern} \hfill Nov 2023 - Jan 2024 \\
TechWave, Jalgaon
\begin{itemize}
    \item Designed and implemented dynamic web applications using web technologies, reducing page load by 35\%.
    \item Collaborated with cross-functional teams to gather requirements and deliver solutions that met client needs, leading to a 40\% increase in client satisfaction.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\textbf{VR Travelling Website}
\begin{itemize}
    \item Played a crucial role in content creation, curating immersive experiences with 360-degree footage and interactive elements.
    \item Designed engaging narratives for each destination.\href{https://vr-travelling-website.vercel.app/}{(Try it here)}
\end{itemize}

\textbf{AI ChatBot}
\begin{itemize}
    \item Developed an AI Chatbot during my time at Batu University, showcasing skills in artificial intelligence and natural language processing.
    \item Created user-friendly conversational interfaces and explored innovative technologies.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

{\bf B.Tech in Computer Science (Final Year)}, KCES's College of Engineering and Management \hfill Expected 2025 \\
Relevant Coursework: Data Structures, Algorithms, Database Management, Web Development

{\bf Higher Secondary Education}, Khandesh College Education Society's Moolji Jaitha College \hfill 2020 - 2022

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES
%----------------------------------------------------------------------------------------

\begin{rSection}{EXTRA-CURRICULAR ACTIVITIES}

\textbf{INNOVATEX Coding Club}
\begin{itemize}
    \item Serving as Vice President, played a key role in fostering a vibrant community of tech enthusiasts.
    \item Organized collaborative coding projects, workshops, and knowledge-sharing sessions.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
